Synthesising Concise Termination and Non-Termination Proofs for Bit-Vector Programs

### 2014-07-08 papers/termination/paper.tex
bitvector -> bit-vector

\keywords
Termination, Non-Termination, Program Synthesis,
Lexicographic Ranking Functions, Bitvector Ranking Functions, Floating-Point Ranking Functions.

>>>>

\keywords
Termination, Non-Termination, Program Synthesis,
Lexicographic Ranking Functions, Bit-vector Ranking Functions, Floating-Point Ranking Functions.
